Characterization and Photometric Performance of the Hyper Suprime-Cam Software Pipeline

### 2017-09-12 draft/response_to_referee.txt

We thank the referee for the careful reading and many valuable comments. Here we attached the updated draft
where important changes are highlighted in cyan.

We believe that all the comments and questions from the referee have been addressed, and below are the
detailed response to some of the referee's concerns.

-----
0. About the general comment that this draft resembles a "technical supplement of the hscPipe paper", we
think:
    * SynPipe paper presents important evaluations of the curent HSC data.  These results are useful to
      the general users of HSC instrument.  Given that the hscPipe paper already contains lots of technical 
      details and is quite long, we believe that a separate paper can better draw people's attention to these
      results. 
    * As we now presented in the new Discussion section, as an independent software, SynPipe is being used for
      many scientific goals, both within and outside the SSP community.  For some of them (e.g. Murata et al.
      in prep. about the impact of blended objects in weak lensing analysis), SynPipe is the key technical
      component.  We think it is useful to have a separate paper as reference to the readers of these works
      and the future SynPipe users.  In addition, SynPipe has recently been adopted by the LSST community, and 
      will be used to test the performance of the LSST pipeline.  We think it is useful to summarize the
      developement of SynPipe on the HSC side as an independent paper. 
    * We would like to draw the referee's attention to papers with the similar purpose, e.g. Balrog for the
      DES survey (http://adsabs.harvard.edu/abs/2016MNRAS.457..786S). These papers are proved to be useful and
      well-cited for similar reasons as we stated above.

-----

# 1. Discussion:

We agree with the referee that this work can benefit from a more detailed discussion, which we have added
before the Summary section.  A few relevant points were included in the earlier Summary and Conclusion
section, and have been moved to the new Discussion section.

We emphasize the importance of such synthetic object pipeline for modern cosmology survey, explain again the
philosophy of our desgin, and compare it with other efforts for testing the data reduction pipline.  
Right now, SynPipe is specifically tailored for HSC images, but it will be included in the LSSTpipe in the
near future.  We demonstrate the broad scientific topics that can benefit from SynPipe, and describe the
on-going efforts for further improvements.

-----
# 2 Interpreter Language

The referee is correct that, in general, C++ should be more efficient in the heavy duty data reduction process.
However, SynPipe here mainly works as a special user interface to hscPipe, which is also use Python for
high-level algorithm.  The reason for this choise is described in details in the Section 2 of the technical paper 
for hscPipe (Bosch et al. 2017).  Below is the most relevant paragraph:

    """
    Both the LSST Data Management codebase and the HSC Pipeline are written in a combination of C++ and Python. 
    Flexibility and extensibility are core development goals at all levels of the code-base: we have attempted 
    to make virtually every algorithm not just configurable but replaceable (even by external code). 
    This flexibility is important for LSST in part because many algorithmic choices in LSST processing still 
    require significant research and are under active development.....

    High-level algorithms are written in Python, primarily as subclasses of our Task class...

    Low-level algorithms that perform direct pixel-level processing or other computationally intensive operations 
    are written in C++....
    """

As the referee can see, flexibility and extensibility is the main reason that hscPipe choose to use Python as
the high-level language.  GalSim also uses the same logic.  Since SynPipe 1) directly depends on hscPipe and
GalSim; 2) will develop along with the hscPipe (and LSSTpipe in the future); 3) does not do any low-level
computationally intensive operation, we think it is natural to follow this decision and use Python as our
working language.

The efficiency of SynPipe, as the referee mentioned, certaintly relates to the available cores of the CPU. 
What we meant to explain is that, under the same computational condition, SynPipe test costs similar amount
time as the real data reduction.  Most heavy duty is carried out by hscPipe, so using C or C++ for SynPipe
will not increase the efficiency.  The most time-consuming part of SynPipe test is the injection of synthetic
objects to the individual CCD image.  During this process, the most computationally intensive part is carried
out by GalSim using C++, so using C or C++ for SynPipe here will not increase the efficiency much.  At the
end, we would like to emphasize that the design of SynPipe currently focuses on testing data reduction in the
most reaslistic way, in the future, we will gradually work on increase the efficiency of SynPipe.

Following the suggestion by the referee, we now try to explain this better in Section 2.2, 
Section 3.1, and Section 3.2.3.

-----
# 3.  Missing Definitions

The referee is correct that some of these basic definitions should be explained better.  
Most of these concepts are explained and discussed in great details in the hscPipe paper (Bosch et al. 2017)
and the Data Release 1 Paper (Aihara et al. 2017).  We emphasize the basic definitions of these values at the
end of the introduction section and point the authors to the Bosch+2017 paper for more details.

-----
# 8. p. 7-8: "High level reduction pipeline": as stated more clearly in the hscPipe technical paper (Bosch et
al. 2017). Low-level reduction involves basic image detrending and calibration; high-level processes involves
the ones that generate coadded images and science-ready catalogs.  Now use the same explanation here to be
consistent with the technical paper and provide more details.

-----
# 9. "purity and completeness"

-----
# Minor comments:

### 2017-09-12 draft/ms_v5.tex
Major issue 1

%% ------------------------------------------------------------------------------------ %%
% Packages
\usepackage{url}
\usepackage{natbib}
\usepackage{latexsym}
\usepackage{morefloats}
\usepackage{xspace}
\usepackage[usenames, dvipsnames]{xcolor}
\usepackage{colortbl}
\usepackage{multirow}

@@

    The HSC data are reduced using a pipeline that builds on the prototype pipeline 
    being designed for the Large Synoptic Survey Telescope’s Data Management system
    (\citealt{Ivezic2008, Axelrod2010, Juric2015}) and is described in 
    Bosch\etal (in prep.). 
    DR1 data are reduced by \hscpipe{} \texttt{v4.0.5}. 
    Because\synpipe{} is intrinsically connected to the complex data reduction
    processes in \hscpipe{}, we briefly introduce the main steps below along with a 
    few key HSC/LSST terms.

@@

@@

@@

        \item After \synpipe{} creates the image of the simulated galaxy, it then 
            shifts the image according to is location on the CCD on a pixel-by-pixel 
            basis; \synpipe{} also crops the images when necessary.
            When that task is complete, \synpipe{} adds appropriate noise to the 
            image based on the pixels it covers and the calibration information of 
            the detector, and creates a variance image that reflects the influence 
            of the synthetic object.
            Since each HSC CCD consists of 4 amplifiers, each with different 
            characteristics, \synpipe{} carefully creates a corresponding gain map 
            to provide accurate noise level.
            The added noise only accounts for the additional flux in the synthetic 
            object, and will thus be subdominant compared to the noise already in 
            the image for faint objects.

@@

    Using the infrastructure provided by \hscpipe{}, the user can easily perform these 
    steps in parallel, and the overall efficiency of \synpipe{} is similar to
    the real data reduction process. 
    The data and catalog volumes is also similar to the original data reduction process.

@@

%% ------------------------------------------------------------------------------------ %%
%% Fig: Galaxy Sample
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_galaxy_sample}
    \end{center}
    \caption{
         \textbf{Upper panel}: five-band magnitude distributions of synthetic
         galaxies. (\texttt{lower panel}; from left to right are the \ser{} index, 
         axis ratio, effective radius in arcsec, the $g-r$ and $r-z$ colors).
         }
    \label{fig:galaxy_sample}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %%
%% Fig: Magnitude v.s S/N for stars
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_psf_sn}
    \end{center}
    \caption{
        Relation between input magnitudes (\textbf{left}: $i$-band; \textbf{right}:
        $g$-band) of synthetic stars and the $\log (\mathrm{S}/\mathrm{N})$ measured 
        by \hscpipe{} PSF photometry.
        Filled-contours and open-contours show the distributions for
        stars in both the \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}. 
        Highly blended stars are highlighted using scatter plots.
        The gray dashed line marks $S/N = 5$ which is the detection threshold used 
        by \hscpipe{}.  
        Our 5$\sigma$ point source detection limit is ${\sim}26.5$ mag in $i$-band,
        however we do not reach these magnitudes with our current synthetic stellar 
        input catalog.
        }
    \label{fig:star_sn}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %%
%% Fig: Accuracy of Forced PSF Magnitudes
\begin{figure*}
    \begin{center}
        \includegraphics[width=16cm]{fig/synpipe_psf_mag}
    \end{center}
    \caption{
        Accuracy of the \texttt{hscpipe} PSF photometry for synthetic stars measured
        by the difference between input and output \forced{} PSF magnitudes.
        Plots [a, b, c, d, e] show the results for [$g$, $r$, $i$, $z$, $y$]-band, 
        respectively.
        The left panel in each plot shows the relation between input magnitude and
        magnitude difference.
        Filled and open contours are for the synthetic galaxies 
        from \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}.
        Highly blended objects are highlighted using scattered points.
        The long-dashed lines mark zero magnitude difference, while the pairs of
        dashed lines outline the running-median of PSF magnitude errors
        (including the uncertainties in aperture correction).
        The right panel in each plot shows the distributions of the magnitude 
        differences for objects in \texttt{goodSeeing} (filled) and \texttt{badSeeing}
        (solid line) \tracts{}.
        The dashed lines identify the distribution of highly blended objects.
        }
    \label{fig:psf_mag}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

@@

%% ------------------------------------------------------------------------------------ %%
    %% Other applications
    Here we focused on characterizing the photometric performance of \hscpipe{}.  
    However, \synpipe{} is a flexible tool and is being used for a range of other     
    applications. 
    For instance, Murata\etal (in prep.) uses \synpipe{} to characterize the level of
    blending in the HSC Wide Layer.  
    \citep{Niikura2017} apply \synpipe{} to high-cadence HSC observations of M31 HSC 
    to search for microlensing events. 
    \synpipe{} is also currently being used to estimate the completeness of high-$z$ 
    LBG and Lyman-$\alpha$ emitters (Ono\etal in prep.; Konno\etal in prep.), to 
    check the completeness of high-$z$ LBG pairs as a function of pair separation 
    (Harikane\etal in prep.), to test the completeness of low surface--brightness 
    dwarf galaxies selections (Greco\etal in prep.), and to test magnifications effects
    around nearby clusters (Chiu\etal in prep.).

    %% Future developments
    Both \hscpipe{} and \synpipe{} are undergoing active development. 
    Our plan is to update \synpipe{} to provide a photometric benchmark for
    each HSC survey data release, which will help improve \hscpipe{}.
    At the same time, we are also working on improving the efficiency of \synpipe{}.
    Many users are not necessarily concerned with the subtle effects involved in 
    the image stacking process. 
    Hence, a future implementation of \synpipe{} will include the option of injecting 
    objects directly onto \coadd{} images which will speed up the generation of 
    synthetic data sets. 
    The results shown in this paper demonstrate the utility of the \synpipe{} framework
    in order to perform end-to-end quality control on pipeline products to the level 
    of accuracy needed by large panchromatic surveys.

>>>>

%% ------------------------------------------------------------------------------------ %%
% Packages
\usepackage{url}
\usepackage{natbib}
\usepackage{latexsym}
\usepackage{morefloats}
\usepackage{xspace}
\usepackage[usenames, dvipsnames]{xcolor}
\usepackage{colortbl}
\usepackage{multirow}

%% ------------------------------------------------------------------------------------ %%

@@

    The HSC data are reduced using a pipeline that builds on the prototype pipeline 
    being designed for the Large Synoptic Survey Telescope’s Data Management system
    (\citealt{Ivezic2008, Axelrod2010, Juric2015}) and is described in 
    Bosch\etal (2017). 
    \song{To enhance the flexibility and extensibility of the pipeline, \hscpipe{} 
    is written using a combination of C++ and Python. 
    All computationally intensive pixel-level operations are performed in C++, 
    high-level algorithm and user interface is written in Python.}
    DR1 data are reduced by \hscpipe{} \texttt{v4.0.5}. 
    Because\synpipe{} is intrinsically connected to the complex data reduction
    processes in \hscpipe{}, we briefly introduce the main steps below along with a 
    few key HSC/LSST terms.

@@

        \item \song{\synpipe{} works as a special user interface to \hscpipe{}. 
            It will keep developing along with the \hscpipe{} (and \textttt{LSSTpipe}
            in the future). 
            Since both \hscpipe{} and \galsim{} use Python as high-level language, 
            we also choose to use Python for \synpipe{} to make the frequent 
            interactions among them easy and straightforward. 
            Most of the computationally expensive tasks are handled by the low-level 
            algorithms in \hscpipe{} and \galsim{} in C++, the usage of Python will not 
            affect the overall efficiency of \synpipe{}.
            }

@@

            \item \song{For galaxy using any parametric model, we generate 
                rectangular cutout image too. 
                The model image can be truncated at $N \times R_{\rm e}$ to reduce the 
                size of the cutout and speed up the injection process. 
                In this work, we truncate all \ser{} model at $10 \times R_{\rm e}$. 
                The results presented here are not sensitive to this choice.}

@@

        \item After \synpipe{} creates the image of the simulated galaxy, it then 
            shifts the image according to is location on the CCD on a pixel-by-pixel 
            basis; \synpipe{} also crops the images when necessary.
            When that task is complete, \synpipe{} adds \song{appropriate Poisson 
            noise} to the 
            image based on the pixels it covers and the calibration information of 
            the detector, and creates a variance image that reflects the influence 
            of the synthetic object.
            Since each HSC CCD consists of 4 amplifiers, each with different 
            characteristics, \synpipe{} carefully creates a corresponding gain map 
            to provide accurate noise level.
            The added noise only accounts for the additional flux in the synthetic 
            object, and will thus be subdominant compared to the noise already in 
            the image for faint objects.

@@

    Using the infrastructure provided by \hscpipe{}, the user can easily perform these 
    steps in parallel.  
    \song{
    For \texttt{coadd} images that include the same number of single-\texttt{Visit} 
    data, the overall efficiency of \synpipe{} is similar to the real data reduction
    process under the same computational conditions (e.g. same number of cores). 
    The \texttt{stack.py} and \texttt{multiBand.py} steps should cost very similar 
    amount of time. 
    The single-\texttt{Visit} process is replaced with the injection of synthetic 
    objects. 
    The speed of this step depends on the total number of fake objects injected and 
    the type of the synthetic object (e.g. fake galaxy using \ser{} model costs more 
    time than fake star).
    For tests with reasonable density of fake objects per CCD (e.g. the tests in this 
    work), the injection step costs slightly less time than the actual 
    single-\texttt{Visit} data processing. 
    }
    The data and catalog volumes is also similar to the original data reduction process.

@@

%% ------------------------------------------------------------------------------------ %%
%% Fig: Galaxy Sample
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_galaxy_sample}
    \end{center}
    \caption{
         \textbf{Upper panels} show the five-band magnitude distributions of synthetic
         galaxies. \texttt{lower panels} \song{
         show the \textbf{input} parameters of the \ser{} 
         model; from left to right are the input \ser{} index, axis ratio, effective 
         radius in arcsec, the $g-r$ and $r-z$ colors}).
         }
    \label{fig:galaxy_sample}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %%
%% Fig: Magnitude v.s S/N for stars
\begin{figure*}
    \begin{center}
        \includegraphics[width=\textwidth]{fig/synpipe_psf_sn}
    \end{center}
    \caption{
        Relation between input magnitudes (\textbf{left}: $i$-band; \textbf{right}:
        $g$-band) of synthetic stars and the $\log (\mathrm{S}/\mathrm{N})$ measured 
        by \hscpipe{} PSF photometry.
        Filled-contours and open-contours show the distributions for
        stars in both the \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}. 
        Highly blended stars \song{with $b>0.05$} are highlighted using scatter 
        plots.
        The gray dashed line marks $S/N = 5$ which is the detection threshold used 
        by \hscpipe{}.  
        Our 5$\sigma$ point source detection limit is ${\sim}26.5$ mag in $i$-band,
        however we do not reach these magnitudes with our current synthetic stellar 
        input catalog.
        }
    \label{fig:star_sn}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %%
%% Fig: Accuracy of Forced PSF Magnitudes
\begin{figure*}
    \begin{center}
        \includegraphics[width=16cm]{fig/synpipe_psf_mag}
    \end{center}
    \caption{
        Accuracy of the \texttt{hscpipe} PSF photometry for synthetic stars measured
        by the difference between input and output \forced{} PSF magnitudes.
        Plots [a, b, c, d, e] show the results for [$g$, $r$, $i$, $z$, $y$]-band, 
        respectively.
        The left panel in each plot shows the relation between input magnitude and
        magnitude difference.
        Filled and open contours are for the synthetic galaxies 
        from \texttt{goodSeeing} and \texttt{badSeeing} \tracts{}.
        Highly blended stars \song{with $b>0.05$} are highlighted using scattered 
        points.
        The long-dashed lines mark zero magnitude difference, while the pairs of
        dashed lines outline the running-median of PSF magnitude errors
        (including the uncertainties in aperture correction).
        The right panel in each plot shows the distributions of the magnitude 
        differences for objects in \texttt{goodSeeing} (filled) and \texttt{badSeeing}
        (solid line) \tracts{}.
        The dashed lines identify the distribution of highly blended objects.
        }
    \label{fig:psf_mag}
\end{figure*}
%% ------------------------------------------------------------------------------------ %%

@@

%% ------------------------------------------------------------------------------------ %%
\section{Discussion}
    \label{sec:discussion}

    \todo{More discussions}
%% ------------------------------------------------------------------------------------ %%
    %% Other applications
    \song{
    Here we focused on characterizing the photometric performance of \hscpipe{}.  
    However, \synpipe{} is a flexible tool and is being used for a range of other     
    applications. 
    For instance, Murata\etal (in prep.) uses \synpipe{} to characterize the level of
    blending in the HSC Wide Layer.  
    \citep{Niikura2017} apply \synpipe{} to high-cadence HSC observations of M31 HSC 
    to search for microlensing events. 
    \synpipe{} is also currently being used to estimate the completeness of high-$z$ 
    LBG and Lyman-$\alpha$ emitters (Ono\etal in prep.; Konno\etal in prep.), to 
    check the completeness of high-$z$ LBG pairs as a function of pair separation 
    (Harikane\etal in prep.), to test the completeness of low surface--brightness 
    dwarf galaxies selections (Greco\etal in prep.), and to test magnifications effects
    around nearby clusters (Chiu\etal in prep.).
    }

    %% Future developments
    \song{
    Both \hscpipe{} and \synpipe{} are undergoing active development. 
    Our plan is to update \synpipe{} to provide a photometric benchmark for
    each HSC survey data release, which will help improve \hscpipe{}.
    At the same time, we are also working on improving the efficiency of \synpipe{}.
    Many users are not necessarily concerned with the subtle effects involved in 
    the image stacking process. 
    Hence, a future implementation of \synpipe{} will include the option of injecting 
    objects directly onto \coadd{} images which will speed up the generation of 
    synthetic data sets. 
    The results shown in this paper demonstrate the utility of the \synpipe{} framework
    in order to perform end-to-end quality control on pipeline products to the level 
    of accuracy needed by large panchromatic surveys. 
    }

@@
